### 2021-02-01 README.Rmd
Fixed all testthat errors related to factors

```{r}
growth_ex <-
  compute_growth(
    census_1 = census_1_ex,
    census_2 = census_2_ex %>% filter(!str_detect(codes, "R")),
    id = "ID"
    ) %>%
  mutate(sp = to_any_case(sp) %>% factor())
```

>>>>

```{r}
growth_ex <-
  compute_growth(
    census_1 = census_1_ex %>% 
      mutate(sp = to_any_case(sp) %>% factor()),
    census_2 = census_2_ex %>% 
      filter(!str_detect(codes, "R")) %>% 
      mutate(sp = to_any_case(sp) %>% factor()),
    id = "ID"
  )
```
